\sysfull

### 2018-04-15 paper/implementation.tex
added placeholder for partial commit
paging figure
Table 2 revised (ready) and API complete

@@

Coala's API adds only 5 syntactic constructs to C-based languages: \texttt{COALA\_TASK}, used to declare a new task; \texttt{COALA\_PV}, used to declare a new protected variable; \texttt{COALA\_NEXT\_TASK} used to mark the next task to be scheduled after the currently executing one completes; \texttt{RP}, used to mark a protected variable read; \texttt{WP}, used to mark a protected variable write.

Moreover, the programmer is required to explicitly call two API functions inside the main body: \texttt{COALA\_INIT}, passing the global initialization task to run upon the first boot as argument; \texttt{COALA\_RUN}, which hands the control to Coala's scheduler.

Finally, when the programmes intends to typedef a struct, to use it as a protected variable, they need to declare each structure's member by using the following macro: \texttt{COALA\_SM}, used to ensure proper memory alignment required by Coala's page handler.

The following table summarizes Coala's API methods and their arguments. $T$ denotes the set of all tasks, while $V$ denotes the set of all protected variables. These methods trigger specific kernel functions, whose detailed implementation is given in the next paragraph.

\begin{table}
\centering
\begin{tabular}{| c | c |}
	\hline
	\textbf{Method} & \textbf{Arguments} \\
	\hline\hline
	\texttt{COALA\_TASK}($t$, $w_t$) & $t \in T$: new task name, $w_t$: weight of task $t$ \\
	\hline
	\texttt{COALA\_PV}(type, $v$ [, size]) & type: var. type, $v \in V$: new protected var. name, size (optional)  array size\\
	\hline
	\texttt{COALA\_NEXT\_TASK}($t$) & $t \in T$ : next task to schedule\\
	\hline
	$u$ := RP($v$) & $v \in V$: protected variable to be read, $u$: value \\
	\hline	
	WP($v$) := $u$ &  $v \in V$: protected variable to be written, $u$: value \\
	\hline
	\texttt{COALA\_INIT}(t) & $t \in T$: task to be scheduled on first boot \\
	\hline
	\texttt{COALA\_RUN}() & {} \\
	\hline
	\texttt{COALA\_SM}(type, $m$ [, size]) &  type: struct member's type, $m$: struct member's name, size (optional): array size \\
	\hline
\end{tabular}
\caption{Coala API}
\label{table:coala_api}
\end{table}

An example usage of Coala’s API is given in the following code snippet. (TBW)

\subsection{Kernel functions implementation}

New tasks. The API method \texttt{COALA\_TASK} statically allocates a non-volatile constant variable holding the task weight, and declares a void function with the name passed as an argument.

@@

\subsection{Paging}

@@

\begin{figure}
	\caption{Illustration of page tags \textcolor{red}{to be drawn}}
\end{figure}

@@

\subsection{Scheduling and committing}

@@

>>>>

We proceed with the explanation of the implementation of \sys programming model. \sys implementation is light and adds very little on top of a plain C language.

\subsection{\sys Application Programming Interface}
\label{sec:coala_api}

Coala's API adds only five syntactic constructs to a C-based language: (i) \texttt{COALA\_TASK}: declaration of a new task, (ii) \texttt{COALA\_NEXT\_TASK}: declaration of the next task to be scheduled after the currently executing one completes, (iii) \texttt{COALA\_PV}: declaration of a new protected variable, (iv) \texttt{RP}: declaration of a protected variable read, and (v) \texttt{WP}: declaration of a protected variable write. Moreover, the programmer is required to explicitly call two \sys API functions inside the main program body: (i) \texttt{COALA\_INIT}: to pass as an argument the global initialization task to run upon the first boot , and (ii) \texttt{COALA\_RUN}: which hands the control to \sys's scheduler. Finally, when the programmer intends to \texttt{typedef} a \texttt{struct} to use it as a protected variable, she/he need to declare each structure's member by using the \texttt{COALA\_SM} macro to ensure proper memory alignment required by \sys's page handler.

Table~\ref{table:coala_api} summarizes \sys's API methods and their arguments. \todo{Add example of a Coala program}{Carlo, Przemek} These methods trigger specific \sys kernel functions, whose explanation is given in the following sections.

\begin{table}
\centering
\begin{tabular}{| r | p{0.7\columnwidth} |}
	\hline
	{Method} & {Arguments} \\
	\hline\hline
	\texttt{COALA\_INIT}(t) & $t \in \mathbf{T}$: task to be scheduled on a first boot \\
	\hline
	\texttt{COALA\_RUN}() & --- \\
	\hline
	\texttt{COALA\_TASK}($t$, $w_t$) & $t \in \mathbf{T}$: new task name, $w_t$: weight of task $t$ \\
	\hline
	\texttt{COALA\_NEXT\_TASK}($t$) & $t \in \mathbf{T}$ : next task to be scheduled\\
	\hline
	\texttt{COALA\_PV}($p$, $v$ [, $s$]) & $p$: variable type, $v \in \mathbf{V}$: new protected variable name, $s$: array size\\
	\hline
	$u$ := \texttt{RP}($v$) & $v \in \mathbf{V}$: protected variable to be read, $u$: value \\
	\hline	
	\texttt{WP}($v$) := $u$ &  $v \in \mathbf{V}$: protected variable to be written, $u$: value \\
	\hline
	\texttt{COALA\_SM}($p$, $m$ [, $s$]) & $p$: \texttt{struct} member's type, $m$: \texttt{struct} member's name, $s$: array size \\
	\hline
\end{tabular}
\caption{Summary of \sys API; $\mathbf{T}$: set of all tasks, $\mathbf{V}$: set of all protected variables, $[, s]$: optional argument.}
\label{table:coala_api}
\end{table}

\subsection{\sys Kernel Functions Implementation}

@@

\textbf{New tasks.} The API method \texttt{COALA\_TASK} statically allocates a non-volatile constant variable holding the task weight, and declares a void function with the name passed as an argument.

@@

\subsection{\sys Paging}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{figures/graffle/paging.pdf}
	\caption{Illustration of page tags \textcolor{red}{to be drawn}}
\end{figure}

@@

\subsection{\sys Scheduling and Committing}

@@

\textcolor{red}{API of the partial commit needs to be explained as well}
